Comparing ChatGPT-4 to Physicians for Assigning Causes of Death from Verbal Autopsy: A Case Study of 6942 Deaths in Sierra Leone from 2019-2022

### 2024-01-25 manuscript/manuscript.tex
Add sections for age groups in va data

This study uses 6939 physician agreed records of 11,920 records collected in 2019 to 2022 from the Healthy Sierra Leone (HEAL-SL) study as described in Section \ref{methods-phyagree}. Section \ref{methods-models} describes the four models, ChatGPT-3.5, ChatGPT-4, InterVA-5, and InSilicoVA, for COD assignment, and their inputs and outputs, while section \ref{methods-eval} details the performance evaluation of the four models relative to physicians overall, by ages, and by COD, using population and individual level metrics.

\subsection{Verbal Autopsy Data}\label{methods-phyagree}

@@

@@

\subsection{Overall Performance by Age Groups}\label{results-overall}

>>>>

This study uses 6939 physician agreed records of 11,920 records collected in 2019 to 2022 from the Healthy Sierra Leone (HEAL-SL) study as described in Section \ref{methods-data}. Section \ref{methods-models} describes the four models, ChatGPT-3.5, ChatGPT-4, InterVA-5, and InSilicoVA, for COD assignment, and their inputs and outputs, while section \ref{methods-eval} details the performance evaluation of the four models relative to physicians overall, by ages, and by COD, using population and individual level metrics.

\subsection{Verbal Autopsy (VA) Data}\label{methods-data}

@@

\subsubsection{Adult VA Records (12 Years or Older)}\label{methods-data-adult}

\subsubsection{Child VA Records (28 Days to 11 Years)}\label{methods-data-child}

\subsubsection{Neonatal VA Records (Under 28 Days)}\label{methods-data-neo}

@@

\subsection{Overall Performance}\label{results-overall}
